Ages of Planets and Stars Observed by Kepler

### 2024-04-04 paper/ms.tex
add <1gyr table maker

\subsection{Sanity Checks}
To date, four stellar clusters in the Kepler field have yielded planet
detections.
They are:...
Young Kepler systems with the most precisely measured ages are...

@@

>>>>

\subsection{Young Planets}

To date, four stellar clusters in the Kepler field have yielded planet
detections.
They are:...
Young Kepler systems with the most precisely measured ages are...

@@

\startlongtable
\begin{deluxetable}{lllrrrr}
	%\tabletypesize{\footnotesize}
	\tabletypesize{\scriptsize}
	\tablecaption{Young planets and planet candidates.
		%The non-truncated machine readable versions are accessible both
		%through the online journal, and at
		%\url{https://zenodo.org/record/8327508}.
		\label{tab:youngplanets}}
	%\toprule
	%\midrule
	%\endhead
	\startdata
	KOI & Kepler & $t_{\rm gyro}$ & $R_{\rm p}$ & $P$ & $f_{\rm RUWE}$ & $f_{\rm grazing}$ \\
	-- &   -- & Myr &    Earths &    days &      bool &   bool  \\
	\hline
	\input{table_subgyr_confirmed} %\\
	%\hline
	\input{table_subgyr_candidate}
	\enddata
	\tablecomments{This table includes X, Y, Z... The machine-readable version,
		available online, includes additional columns for .... 
	}
\end{deluxetable}
%\endlongtable
